IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/conclusion.tex

\cut{
\section{Conclusion}
\label{sec:conclusion}

In this paper, we develop a general coarse-grained approach to IFC
based on dividing a system into relatively course computational units
and tracking only communication between these isolated units.
We give formal semantics for the core coarse-grained
information flow control language and show how a large class of target languages
can be combined with it to achieve provable
non-interference.
We then give a proof technique for showing  non-interference
of a concrete semantics for a potentially optimized IFC language
by means of an isomorphism, and identify a class of IFC language restrictions
that preserves non-interference.
We briefly describe ways to enrich the core IFC language with
more advanced concepts such as labeled values, privileges, or a
notation of clearance and
connect our formal semantics to real implementations of
coarse-grained IFC systems for Javascript, Haskell, and
(in less detail) enforcing IFC in C.
Leaving more detailed presentation to later work,
we informally relate our results to a monadic interpretation
of IFC which guided our design.
}

>>>>

%\cut{
\section{Conclusion}
\label{sec:conclusion}

We present a formal semantics which describes how to extend arbitrary languages
with language-based coarse-grained IFC. We provably show the security guarantees
TSNI and TINI non-interference, where the proof technique is parametrized on the
target language, and it is developed for two ubiquitous scheduling policies. In
addition, we provide conditions to securely refine our formal semantics to
consider optimizations required in practice. Finally, we describe extensions to
the core IFC language with more advanced concepts like labeled values, privileges,
and a notation of clearance, and therefore connecting it with existing
IFC implementations for Javascript, Haskell, and (in
less detail) proposing IFC for C.

With this work, we set a global framework which describes how ideas from
OS can be systematically applied in programming languages.

% In this paper, we develop a general coarse-grained approach to IFC
% based on dividing a system into relatively course computational units
% and tracking only communication between these isolated units.
% We give formal semantics for the core coarse-grained
% information flow control language and show how a large class of target languages
% can be combined with it to achieve provable
% non-interference.
% We then give a proof technique for showing  non-interference
% of a concrete semantics for a potentially optimized IFC language
% by means of an isomorphism, and identify a class of IFC language restrictions
% that preserves non-interference.
% We briefly describe ways to enrich the core IFC language with
% more advanced concepts such as labeled values, privileges, or a
% notation of clearance and
% connect our formal semantics to real implementations of
% coarse-grained IFC systems for Javascript, Haskell, and
% (in less detail) enforcing IFC in C.
% Leaving more detailed presentation to later work,
% we informally relate our results to a monadic interpretation
% of IFC which guided our design.
% }
